{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-05-05 TechDoc/TechDoc.tex
Add to future improvements

\subsubsection{Future Improvements}

>>>>

\subsubsection{Future Improvements}
The gene models track could be expanded to display alternative splicing events, offering a clearer view of transcript diversity. Additionally, adding a hover-based popup over each bin that displays gene models for accessions containing variants could offer a rapid and informative view of variant differences.
